What do incoming university students believe about open science practices in

### 2021-02-24 analysis/Manuscript.Rmd
continue with demographics

# note re: exclusion [all coded in `exclude` in preprocessing, 
# but need to summarise exclusion criteria here]
  # exclude those who are younger than 18 [7]
  # only those who say "1" to eligibility are included; all other responses are excluded
  # those whose `status` variable is an 'IP Address' are included

@@

```{r demographics}

# gender --> need to run through gendercoder
# high school status
# high school psyc 
# country of university 
# country of nationality
# whether parents' attended uni

@@

Of the remaining `r n` participants, most reported that they were
18-24 years old (*n* = `r age[2,2]`), `r age [3,2]` 
reported that they were 25-34 years old, `r age [4,2]` were 35-44 years old,
`r age [5,2]` were 45-54 years old, `r age [6,2]` were 55-64 years old, and
`r age [7,2]` were 65 years or older.

>>>>

# note re: exclusion [all coded in `exclude` in preprocessing, 
# but need to summarise exclusion criteria here]

@@

```{r demographics for those included in analyses}

# age
age <- df %>% dplyr::count(age_lab)

# gender --> need to run through gendercoder [breadcrumb!]

# high school status
hs_status <- df %>% dplyr::count(high_school_lab)

# high school psyc 
hs_psyc <- df %>% dplyr::count(psych_hs_lab)

# country of university 
uni_country <- df %>% dplyr::count(uni_country)

# country of nationality
nationality <- df %>% dplyr::count(nationality)

# whether parents' attended uni
first_gen <- df %>% dplyr::count(first_gen_lab)
```

@@

Of the remaining `r n` participants, most reported that they were
18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old. ADD GENDER HERE!

Nearly all reported that they graduated from high
school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
attended high school, a little less than half completed psychology courses in 
high school (*n* = `r hs_psyc[2,2]`). In terms of their nationality, most 
participants reported that they were Australian (*n* = `r nationality[3,2]`), 
from the United Kingdom (*n* = `r nationality[24,2]`), or Chinese 
(*n* = `r nationality[6,2]`). In terms of where the participants were attending 
university, most reported that they were in Australia (*n* = `r uni_country[1,2]`), 
the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). 
Finally, about 2/3rds of participants reported that at least one of their parents 
attended university (*n* = `r first_gen[2,2]`).
